---
title: "Exercises"
output: html_document
---

```{r load packages}
library(tidyverse)
```

#Exercise 1 (Group)

Together as a group, we'll go through a complete cycle of the github workflow to contribute to code.
```{r make a function to multiply by three}
mult5 <- function(x){
  return()
}

mult3(2) #Should return the value 10
```

#Exercise 2 (Breakout Room - part 1)
Complete the function so that it adds the value five to a given input, x.
Person 1 should make the c
```{r}
add5 <- function(x){
  return()
}

add5(10) # Should return the value 10
```

#Exercise 2 (Breakout Room - part 2)
Complete function so that it divides a given input, x, by the value 2
```{r}

div2 <- function(x){
  return()
}

div2(20) # Should return the value 10
```

#Exercise 3 (Group)
Complete the function so that it returns an input, x, to the power of 2
```{r}
power2 <- function(x){
  return()
}

power2(5) #Should return 25
```

#Exercise 4 (Breakout Room - part 1)
Complete the function so that it returns the square root of an input value, x.
```{r}
square_root <- function(x){
  return()
}

square_root(144) #Should return the 12
```

#Exercise 4 (Breakout Room - part 2)
Complete the function so that it returns the sum of a given input vector, x.
```{r}
sum_all <- function(x){
  return()
}

sum_all(x = c(1,2,3)) #Should return 6
```