---
title: "GH_flow_practice"
output: html_document
---

#Introduction to GitHub Flow

See git-cheat-sheet.pdf file in the repository.

##Setup Demo (In Group)

As we go through the demo together, Charreau will be "Person 1" and Umang will be "Person 2".

1. Person 1's repository will be used for the remaining exercises. 
2. Person 1 adds person 2 as an admin in their repository.
3. Person 2 clones person 1's github repository, and using the git URL creates a new RStudio project.


##Exercise 1 (In Group)

Together as a group, we'll go through a complete cycle of the GH Flow to contribute to code. In this set, we'll create a new repository using a template, clone the repository, and make code contributions to it. 

```{r make a function to multiply by three}
mult3 <- function(x){
  return()
}

mult3(2) #Should return the value 6
```

##Setup (In small groups)
1. Person 1's repository will be used for the remaining exercises. 
2. Person 1 adds person 2 as an admin in their repository.
3. Person 2 clones person 1's github repository

##Exercise 2 Part 1 (In small group - person 1)

Complete the function so that it adds the value five to a given input, x.
Person 1 should make the change in code, and person 2 should manage the pull request.

###Steps

*Person 1:*

1. Create new branch (top right corner, git tab, branch icon). Name the branch "Exercise-2". The defaults settings work.

2. Complete the function below. Save your work.

3. Stage - click box beside file name in the git window.

4. Commit - Write a commit message that completes the statement "With this commit I"....

5. Push - click the "up" arrow in the git tab to send your changes to the remote repository. 

6. In the GitHub repository, make a Pull Request for the change.

*Person 2:*
7. Person 2 manages the pull request, merges and closes it. (In actuality/real world, we'd test the code before closing the pull request.)

```{r person one codes}
add5 <- function(x){
  return()
}

add5(10) # Should return the value 15
```

##Exercise 2 Part 2 (In small group - person 2)

Follow the above steps, but now switch roles: person 2 do steps 1 - 6 for the function below, and person 1 do step 7.  Person 2 should begin by first clicking Pull (down arrow) to update your local repository with the remote changes.

Complete function so that it divides a given input, x, by the value 2.
Person 2 should make the change in code, and person 1 should manage the pull request.

```{r person two codes}

div2 <- function(x){
  return()
}

div2(20) # Should return the value 10
```

##Exercise 3 (Group)

Now, we will go through the same steps again, but using the command line. Charreau will be "person 1" and "Umang will be person 2". 

Complete the function so that it returns an input, x, to the power of 2. 

```{r make function to square a value}
power2 <- function(x){
  return()
}

power2(5) #Should return 25
```

##Exercise 4 (In small group - Part 1)

Complete the function so that it returns the square root of an input value, x.

Person 1 should make the change in code, and person 2 should manage the pull request.

*Person 1:*

1. Create a new branch named "Exercise-4" using the following commands:

git checkout -b exercise-4 
git push -u origin exercise-4

Check to see what branch you're on using: git branch
Check the status of your git repository using: git status

2. Complete the function below. Save your work.

3. Stage changes using the following command:

git add GH_flow_practice.Rmd

4. Commit - Write a commit message (replace 'commit_msg' in the command below) that completes the statement "With this commit I"... and execute the following command:

git commit -m "commit_msg"

5. Push - Send your changes to the remote repository using the following command.  You'll have to enter your github credentials:

git push origin exercise-4

6. In the GitHub repository, make a pull request for the change.

*Person 2:*

7. Person 2 manages the pull request, merges and closes it. (In actuality/real world, we'd test the code before closing the pull request.)


```{r make function for square root of value}
square_root <- function(x){
  return()
}

square_root(144) #Should return the 12
```

##Exercise 4 (In small group - Part 2)

Complete the function so that it returns the sum of a given input vector, x.

Person 2 should make the change in code, and person 1 should manage the pull request.

Follow the above steps, but now person 2 do steps 1 - 6 for the function below, and person 1 do step 7.  Person 2 should begin by first running the command:

git pull origin master

to update your local repository with the remote changes.

```{r make function for sum of vector}
sum_all <- function(x){
  return()
}

sum_all(x = c(1,2,3)) #Should return 6
```
